
The formation of stars is filled with filamentary, fractal structure.  The
\nameCores\ project will study the behavior of collapsing gas as it transitions
from fractal structures to form dense prestellar cores.  We will motivate the
simulation in Section \ref{subsec.cores_motivate} and describe the simulations
in \ref{subsec.cores_sims}.


\subsubsection{Motivation: \nameCores}
\label{subsec.cores_motivate}
The formation of stars is one of the most important processes in astrophysics,
as stars provide most of the light we see in the night sky, and they produce the metal and energy
that dictates the structure and composition of a galaxy.  It is also poorly
understood, as it is driven by primarily the chaotic dynamics of the turbulent
interstellar medium (ISM).   A \emph{prestellar core} is a knot of dense gas
formed by gravity in a molecular cloud, which will ultimately form a star.  The
formation of these cores is one of the more difficult puzzles in star formation,
as it is fundamentally dictated by chaotic dynamics of the turbulence in the
cloud.  This is the focus of the \nameCores\ project.

One of our previous studies examined the collapse of a molecular cloud by
including semi-Lagrangian tracer particles that follow the flow.  The particles
that are found in dense cores are then used to run the simulation "backwards",
to examine the \emph{preimage} of the gas, before it collapses.  This will allow
us to better constrain star formation models.  (Collins et al 2022, in prep)

One of the curios findings is the fractal nature of the preimage gas.  We find
that gas from distinct cores at the end of the simulation begins life mixed with
one another in a fractal manner. This can be seen in Figure
\ref{fig.cores}, which shows the the overlap of a collection of preimages at the
beginning of the simulation in the first 3 panels, and the
collapse to form dense cores in the fourth.  The length scale in the first three panels translates to
roughly 2 pc in size.  These panels show the overlap and fractal, filamentary nature of
the gas before it collapses.  The
last panel shows the un-mixing of the gas as it collapses in time.

\subsubsection{Simulations: \nameCores}
\label{subsec.cores_sims}

The simulation presented in Figure \ref{fig.cores} was one of a suite of three
simulations with varied magnetic field strength.  These simulations were
relatively low resolution as we developed the analysis techniques and learned
about extended nature of the primage gas.
Our proposed simulations will greatly improve the resolution of our simulations,
to explore if these structures are in fact fractal, or a result of low
resolution. The target simulations will have $512^3$ root grid and 4 levels of
AMR, and $1024^3$ particles.  This is an increase of 4 in linear scale for the
gas, and 16 for the particles over the results shown in Figure \ref{fig.cores}.
The proposed suite of three simulations will mirror the preliminary in magnetic
field strength.  


